%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[ngerman]{babel}
\usepackage{ragged2e}

\addbibresource{bibliography.bib}

%\usepackage{mathtools}
\SetLabelAlign{center}{\clap{#1}}

\begin{document}
\header{jannis}{krämer}
       {mobile developer with testing experience}


% In the aside, each new line forces a line break
\onehalfspace

\begin{aside}
  \section{about}
  \begin{itemize}[leftmargin=0pt,align=center,labelsep=1.5em]
      \item[{\FA \symbol{"F1FD}}] 10. März 1995
      \item[] in Saarlouis
  \end{itemize}

  \section{contact}
    Tilsiter Straße 2f
    22049 Hamburg
    ~
    \faEnvelope \ \href{mailto:jannis@4kraemer.me}{jannis@4kraemer.me}
    \href{http://4kraemer.me}{http://4kraemer.me}
    %\href{http://twitter.com/johnderate}{twitter://@johnderate}
    \faLinkedin \ \ \href{http://linkedin.com/in/jannis-kraemer}{jannis-kraemer}
    \faGithub \ \ \href{https://github.com/Johnderate}{Johnderate}
    ~
  \section{languages}
    german native speaker
    english fluent speaker
    ~
  \section{programming}
    \faCode \ Java {\color{red} \faHeart}, C\# {\color{red} \faHeart}, Racket
    \faMobile \ \ Android {\color{red} \faHeart}
    \faHtml5 \ \ HTML5, CSS3
    \faLaptop \ \ macOS {\color{red} \faHeart}, Linux, Windows
    \faDatabase \ \ MySQL, MSSQL
    \faCodeFork \ \ Git, Team Foundation Server
\end{aside}

\section{interests}
  \subsection{work}
    mobile applications, software testing, game development, web development
  \subsection{private}
    games, singing (classical), political science


\section{experience}

\begin{entrylist}
  \entry
    {02–10 2016}
    {Orange Networks, Hamburg}
    {Software Tester}
    {\emph{Testing of an application for software deployment, used e.g. in Hamburgs authorities and at Dataport.}\\
    Written a custom Framework for Microsoft Coded UI Tests.} \\
  \entry
    {06–07 2015}
    {Gelehrtenschule des Johanneums, Hamburg}
    {Teaching}
    {\emph{Teaching computer science in extracurricular course.}\\
    Taught a class of 18 students Java and Web Development}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {since 2014}
    {B.Sc. {\normalfont in Computer Science}}
    {University of Hamburg}
    {Volunteering as student representative and in the orientation unit}
  \entry
    {2006 - 2014}
    {Abitur}
    {Gelehrtenschule des Johanneums}
    {Awarded by the German Physical Society for the second best Abitur in physics.}
\end{entrylist}

\section{applications}

\begin{entrylist}
 \entry
    {2016}
    {AutoSW 2}
    {\href{https://www.autosw.de/Demo/Benefit}{autosw.de}}
    {An automated deployment and life cycle management solution for software, operating systems and devices.}
\end{entrylist}

\section{volunteering}

  \begin{entrylist}
    \entry
      {since 2015}
      {St. Jacobi Principal Church, Hamburg}
      {\href{http://www.jacobus.de}{jacobus.de}}
      {Church choir (Kantorei St. Jacobi) and lector}
    \entry
      {since 2014}
      {University of Hamburg, Department of Informatics}
      {\href{https://www.inf.uni-hamburg.de/en.html}{inf.uni-hamburg.de}}
      {Student representative and orientation unit}
  \end{entrylist}
%%% Nothing to see here!
%\section{publications}
%
%Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors.
%
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
